Verifying Demonstrations

### 2018-02-05 paper/properties.tex
Improves {requirements} and {properties} environments

We desire three verifiability requirements:
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each 
  participation proof provides temporal and spatial eligibility and that it has 
  not been counted before.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the submitted participation proofs.
\item\label{IndividualVerif} Individual verifiability: every participant can 
  verify that their participation proof is included in the global count.
\end{requirements}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to verify that each proof is indeed related to the 
event.
We must associate the proof to the event both spatially (the correct location) 
and temporally (it is related to the time-interval of the event).
We can essentially divide it into the following requirements:
\begin{requirements}[\ref*{EligibilityVerif}.]
  \item Temporal egligibility:%
    \label{CreatedAfterStart} prove that the data was created after the start of 
    the event;%
    \label{CreatedBeforeEnd} prove that the data was created before the end of 
    the event.
  \item Spatial eligibility:%
    \label{SpatiallyRelated} prove that the data is spatially related to the 
    physical location of the event.
  \item One-proof-per-person:%
    \label{CountOnce} prove that no individual can be counted more than once.
  \item Designated event:%
    \label{DesignatedEvent} prove that the data is designated for the event.
\end{requirements}

@@

\begin{definition}[Proof indistinguishability]
  \dots
\end{definition}

@@

\begin{definition}[Receipt freeness/deniability]
  \dots
\end{definition}

>>>>

We desire three verifiability requirements:

\begin{requirements}[V]
  \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
    participation proof provides temporal and spatial eligibility and that it 
    has not been counted before.
    \begin{requirements}
    \item Temporal egligibility:%
      \label{CreatedAfterStart} prove that the data was created after the start of 
      the event;%
      \label{CreatedBeforeEnd} prove that the data was created before the end of 
      the event.
    \item Spatial eligibility:%
      \label{SpatiallyRelated} prove that the data is spatially related to the 
      physical location of the event.
    \item One-proof-per-person:%
      \label{CountOnce} prove that no individual can be counted more than once.
    \item Designated event:%
      \label{DesignatedEvent} prove that the data is designated for the event.
    \end{requirements}

  \item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
    result is according to the submitted participation proofs.
  \item\label{IndividualVerif} Individual verifiability: every participant can 
    verify that their participation proof is included in the global count.
\end{requirements}
We will now discuss these in more detail.

@@

\begin{definition}[Proof indistinguishability]
  Adversary chooses two messages \(m_0, m_1\) and gives them to the challenger.
  Challenger uniformly randomly selects \(b\rgets \bin\) and runs \(c_b \gets 
    PRF_k(m_0), c_{1-b} \gets PRF_k(m_1)\).
  The challenger gives \(c_0, c_1\) to adversary.
  If the adversary outputs \(b' = b\) she wins.
  (The property should be similar to key privacy~\cite{KeyPrivacy}.)
\end{definition}

@@

\begin{definition}[Receipt freeness/deniability]
  Adversary gets oracle access to the user?
  User provides a witness?
\end{definition}
